Species motif participation provides unique information about species risk of extinction

### 2023-04-18 manuscript/JAE_reply.tex
Updates from Overleaf

            \item Introduction Line 13-16: The wording here makes it seem like species loss is both the stressor/disturbance and the response variable. This would be clearer if the authors clarify whether they are studying the effects of disturbance at the primary producer level on consumer persistence right away. It would also be helpful to define exactly what definition of disturbance they are referring to in the introduction.

                \textbf{R:}
            The sentence the reviewer refer to is "How disturbances such as population decline or extinction lead to the loss of species via  direct and indirect effects (i.e., secondary extinctions) has long been a vibrant area of research (Curtsdotter et al., 2011a; Dunne & Williams, 2009; Eklöf \& Ebenman, 2006 Santos et al., 2021)." We can understand the reviewer´s confusion, but in fact species extinctions are both the disturbance and the response; an initial extinction of a species (i.e. the primary extinction) can, via species interactions, cause other species to extinct (i.e. secondary extinctions).

>>>>

            \item Introduction Line 13-16: The wording here makes it seem like species loss is both the stressor/disturbance and the response variable. This would be clearer if the authors clarify whether they are studying the effects of disturbance at the primary producer level on consumer persistence right away.

                \textbf{R:}
            The sentence the reviewer refer to is "How disturbances such as population decline or extinction lead to the loss of species via  direct and indirect effects (i.e., secondary extinctions) has long been a vibrant area of research (Curtsdotter et al., 2011a; Dunne & Williams, 2009; Eklöf \& Ebenman, 2006 Santos et al., 2021)." We can understand the reviewer´s confusion, but in fact species extinctions are both the disturbance and the response; an initial extinction of a species (i.e. the primary extinction) can, since species are connected to each other via for example consumer -- resource interactions, cause other species to extinct (i.e. secondary extinctions). We have now clarified this on line XX: 
            "The loss of a species in a food web can, due to the mutual dependencies among species, trigger a cascade of additional extinctions, so called secondary extinctions. A species' position within a food web is known to affect its risk of going secondarily extinct ~\citep{Santos2021,curtsdotter2011robustness, dunne2009cascading, Eklof2006}."

            \item It would also be helpful to define exactly what definition of disturbance they are referring to in the introduction.

             \textbf{R:}
             We have now clarified how we here define a disturbance. This is done on line XX. "The loss of a species in a food web can, due to the mutual dependencies among species, trigger a cascade of additional extinctions, so called secondary extinctions. A species' position within a food web is known to affect its risk of going secondarily extinct ~\citep{Santos2021,curtsdotter2011robustness, dunne2009cascading, Eklof2006}."

### 2023-04-18 manuscript/supplement_motifs.tex
Updates from Overleaf

    % Updated to use mean instead of all species
    \begin{table}[hb!]
        \caption{Coefficients ($\beta$) for models relating persistence to the proportion of a network profile made up by a focal motif, the level of disturbance to basal resources (corresponding to a probability of extinction ranging between 0.1 and 0.5), and their interaction. Coefficients in \textbf{bold} are significant ($\alpha$\textless0.005). Predictors were centered and scaled before model fitting; coefficients refer to a unit increase in predictors. We also provide McFadden's pseudo-$R^2$ value for each regression. }
        \label{motif_profile_tab}
        \centering
        \footnotesize
        \begin{tabular}{c|c c c c c | c }
        Motif & Intercept & Proportion & Disturbance & Interaction &  pseudo-$R^2$ \\
            \hline
            Three-species chain & \textbf{0.326} &  0.0260 & \textbf{-0.595} & -2.53$\times10^{-3}$ & 0.*958 \\
            Apparent competition & \textbf{0.326} & \textbf{0.0501} & \textbf{-0.596} & -2.00$\times10^{-3}$ & 0.962 \\
            Direct competition & \textbf{0.326} & 0.0151 & \textbf{-0.595} & -5.34$\times10^{-4}$ & 0.956 \\
            Omnivory & \textbf{0.326} & \textbf{-0.0626} & \textbf{-0.596} & 3.22$\times10^{-3}$ & 0.966 \\
        \end{tabular}
    \end{table}
\clearpage

>>>>

    % Updated to use mean instead of all species
    \begin{table}[hb!]
        \caption{Coefficients ($\beta$) for models relating persistence to the proportion of a network profile made up by a focal motif, the level of disturbance to basal resources (corresponding to a probability of extinction ranging between 0.1 and 0.5), and their interaction. Coefficients in \textbf{bold} are significant ($\alpha$\textless0.005). Predictors were centered and scaled before model fitting; coefficients refer to a unit increase in predictors. We also provide McFadden's pseudo-$R^2$ value for each regression. }
        \label{motif_profile_tab}
        \centering
        \footnotesize
        \begin{tabular}{c|c c c c c | c }
        Motif & Intercept & Proportion & Disturbance & Interaction &  pseudo-$R^2$ \\
            \hline
            Three-species chain & \textbf{0.326} &  0.0260 & \textbf{-0.595} & -2.53$\times10^{-3}$ & 0.958 \\
            Apparent competition & \textbf{0.326} & \textbf{0.0501} & \textbf{-0.596} & -2.00$\times10^{-3}$ & 0.962 \\
            Direct competition & \textbf{0.326} & 0.0151 & \textbf{-0.595} & -5.34$\times10^{-4}$ & 0.956 \\
            Omnivory & \textbf{0.326} & \textbf{-0.0626} & \textbf{-0.596} & 3.22$\times10^{-3}$ & 0.966 \\
        \end{tabular}
    \end{table}
\clearpage
